%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  One Page Two Column Resume
% LaTeX Template
% 
%
% Original author:
% Aditya Kharade
%
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 



\documentclass[]{resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Aditya}{Kharade}{ \urlstyle{same} \href{https://www.salesforce.com/trailblazer/aditya196}{Trailblazer Profile} |
\href{https://www.linkedin.com/in/adityakh196/}{LinkedIn Profile}\\
\href{mailto:aditya.kharade@gmail.com}{aditya.kharade@gmail.com} | +919422035458 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Pune University}
\descript{BE in Computer Engineering}
\location{Aug 2016 - August 2020 | Pune, MH}
PES Modern College
Of Engineering
\location{ Cum. GPA: 8.06/10}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Salesforce}

\textbullet{} Apex \newline  \textbullet{}  Lightning Web Components (LWC) \newline \textbullet{} Salesforce Admin \newline \textbullet{} SOQL \newline  \textbullet{} Apex Triggers \newline \textbullet{} Data Loader and Salesforce Inspector \newline \textbullet{} Salesforce Lightning Design System (SLDS) \newline \textbullet{} Debugging \newline \textbullet{} Client communication\newline and requirement gathering \newline \newline

\subsection{Others}
MySQL \textbullet{} R \textbullet{} Python \textbullet{} Data Analytics \\

Tableau \textbullet{} MS Excel \textbullet{} Android \textbullet{} 
\sectionsep


\section{Certifications}
\subsection{Salesforce}

\textbullet{} Salesforce Certified Associate \newline  \textbullet{}  Salesforce Certified Administrator \newline  \textbullet{}  Salesforce Certified Platform App Builder \newline \textbullet{} Salesforce Certified Platform Developer 1 (I) \newline
 \textbullet{} Salesforce Certified Platform Developer 2 (II) 
\newline \newline
\subsection{Others}
\textbullet{} Data Analysis with Python by FreeCodeCamp \newline
\textbullet{} Data Analytics Professional by Google 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Cognizant}
\descript{| Salesforce Developer }
\location{Jan 2021 - Present | Pune, MH}
\sectionsep


\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item  As a Salesforce Developer on a health cloud application client of
Cognizant Technology Solutions, I excel at providing real-time solutions for
critical business deadlines. \newline
\item  Expertise in implementing customization using triggers, apex classes, apex
batches, and more. \newline
\item  Responsible for handling all data-related activities and user support as per
requirement, and transferring basic to advanced knowledge to team members. \newline
\item Exceptional debugging skills and a keen eye fortesting new features in the
system. \newline
\item  Expertise in Salesforce Configuration, including validation rules, data security,
roles, permission sets, process builder, flows, company
information, public groups, case management, lightning app builder, page
layout, object creation, fields, and user management.\newline
\item  Experience in creating sandbox environments for deployments and
post-refresh activities to disconnect with production.\newline
\item Oversee the end-to-end data life cycle within Salesforce, directing major data loading activities including patient record acquisition, validation, and transformation, while ensuring compliance with regulatory standards and internal policies.\newline
\item Collaborate cross-functionally to design and optimize data integration processes, troubleshoot pipeline issues, and implement governance policies, ultimately guaranteeing the accurate and timely loading of patient data into the system.\newline
\item Proficient in user stories creation and backlog prioritization, allowing me to effectively manage tasks and ensure timely delivery of critical  production defects\newline

\item Passion for technology and commitment to delivering high-quality solutions
make me an asset to any team.\newline
\end{tightemize}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\subsection{ALWAYS STRIVING, NEVER SETTLING AWARD}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item I was honored with this award for playing a pivotal role as a key member of the team, driving numerous critical activities, implementing technical processes, and contributing to data analysis, reporting, and management that were instrumental to the success of the team.
\end{tightemize}
\sectionsep



\end{minipage} 
\end{document}  \documentclass[]{article}
